---
title: "Day14"
author: "Olivia Wu"
date: "2024-04-18"
header-includes:
   - \usepackage{amsmath}
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tinytex)
library(readr)
library(ggplot2)
library(BSDA)
library(leaps)
library(olsrr)
library(car)
library(mosaic)
```
```{r, include=FALSE}
setwd("C:/Users/ozwu/OneDrive/Documents/SCHOOL/RS3")
HP <- read_csv("csv/CSV Data Set Files by Descriptive Title/HighPeaks.csv")
SAT <- read_csv("csv/CSV Data Set Files by Descriptive Title/SATGPA.csv")
setwd("Chapter 4")
```

<!-- 5, 9, 13, 15-18 -->

\section*{Problem 5.5}
\quad a) Variance of several groups = True

\quad b) Mean of one group = False

\quad c) Means of several groups = True

\quad d) Variance of one group = False

\section*{Problem 5.9}
The three main reasons to randomize the assignment of treatments to units are:

\quad 1) justify the use of a probability model

\quad 2) Protect against bias and confounding

\quad 3) support inference about cause-and-effect

\section*{Problem 5.13}
\textbf{Major} - Categorical, would have to use ANOVA

\textbf{Sex} - Categorical, can use two-sample $t$ test

\textbf{Class year} - Categorical, would have to use ANOVA

\textbf{Political inclination} - Categorical, would have to use ANOVA

\textbf{Sleep time last night} - Quantitative

\textbf{Study time last week} - Quantitative

\textbf{BMI} - Quantitative

\textbf{Total amount of money spent on textbooks} - Quantitative

\section*{Problem 5.15}
\quad a) Explanatory: font used on exam

\quad Response: final exam score

\quad b) This is an randomized treatment because the instructor actively (and randomly) assigned fonts to her students.

\quad c) The random assignment takes care of the independence condition. \textcolor{red}{Important!!!}

\section*{Problem 5.16}
\quad a) Explanatory: main ingredient in dog food

\quad Response: amount of energy that dogs have

\quad b) This is a randomized experiment because the food ingredient was randomly assigned

\quad c) The random assignment takes care of the independence condition.

\section*{Problem 5.17}
\quad a) The units are each student

\quad b) The treatments are the 4 kinds of fonts: Times, Courier, Helvetica, Comic Sans

\quad c) She would need 10 students in each font category

\section*{Problem 5.18}
\quad a) the units are the dogs

\quad b) the treatments are the kind of main ingredient: salmon, chicken, and beef

\quad c) Each diet needs 15 dogs on it