---
title: "Day17"
author: "Olivia Wu"
date: "2024-04-30"
header-includes:
   - \usepackage{amsmath}
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tinytex)
library(readr)
library(ggplot2)
library(BSDA)
library(leaps)
library(olsrr)
library(car)
library(mosaic)
```
```{r, include=FALSE}
setwd("C:/Users/ozwu/OneDrive/Documents/SCHOOL/RS3")
Hawk <- read_csv("csv/CSV Data Set Files by Descriptive Title/Hawks.csv")
FanBase <- read_csv("csv/CSV Data Set Files by Descriptive Title/FantasyBaseball.csv")
setwd("Chapter 5")
```
<!-- Page 245-254# 8, 10, 43, 49, 67, 69 -->

<!-- For #43 use Weight for your variable -->

\section*{Problem 5.8}
C

\section*{Problem 5.10}
\quad a) The variability within each group changes a lot across groups.

\quad b) The slope tells us which transformation to use after saying $p=1-s$.

\section*{Problem 5.43}
\quad a) The points look like they could fit on a line, but barely.

\quad b) The slope of the line is 0.4298.

\quad c) $p=0.5702$, which suggests a square root transformation.

```{r,echo=FALSE, out.width="60%"}
stat <- favstats(Weight~Species,data=Hawk)[c("Species","mean","sd","n")]
plot(log(stat$sd)~log(stat$mean), pch=19)
abline(lm(log(stat$sd)~log(stat$mean)),col="blue")
```

\section*{Problem 5.49}

\quad a) 

```{r,echo=FALSE}
Hawk$Weight <- sqrt(Hawk$Weight)
```

```{r,echo=FALSE}
favstats(Weight~Species,data=Hawk)[c("Species","mean","sd","n")]
```

\quad b) The average weight tends to be higher for RT, then CH, then SS. 

```{r,echo=FALSE, out.width="60%"}
boxplot(Weight~Species, data=Hawk, horizontal=FALSE)
```

\quad c) The IQR are roughly the same size, suggesting similar variability. There are many outliers for each groups, suggesting a skew. Thus, the normality condition is not met, and an anova test would be inappopriate.

\section*{Problem 5.67}

\quad a) The points on the right do not lie close to the line, there seems to be a curved pattern. This fails the normality condition.

```{r,echo=FALSE, out.width="60%"}
model <- aov(Time~Person, data=FanBase)
qqnorm(model$residuals)
qqline(model$residuals)
```

\quad b) The transformed data fits the line much better, and it has better normality.

```{r,echo=FALSE}
FanBase$LnTime <- log(FanBase$Time)
model <- aov(LnTime~Person, data=FanBase)
qqnorm(model$residuals)
qqline(model$residuals)
```

\section*{Problem 5.69}

```{r,echo=FALSE}
FanBase$Round <- factor(FanBase$Round)
```

Original data: the qqplot is not linear, so normality fails.

```{r, out.width="60%"}
model <- aov(Time~Round, data=FanBase)
qqnorm(model$residuals)
qqline(model$residuals)
```

We check log(s) vs. log(ave): the points are roughly linear, and we see that 1-slope $\approx$ 0.035, so we proceed to use logarithms to transform the data.

```{r, out.width="60%"}
stat <- favstats(Time~Round,data=FanBase)[c("Round","mean","sd","n")]
plot(log(stat$sd)~log(stat$mean), pch=19)
abline(lm(log(stat$sd)~log(stat$mean)),col="blue")
```

Transformed data: The points are much more linear, and they meet the normality condition.

```{r, out.width="60%"}
model <- aov(LnTime~Round, data=FanBase)
qqnorm(model$residuals)
qqline(model$residuals)
```

Anova: $p=0.713 > 0.05$, so we fail to reject the null hypothesis. There is not enough evidence to suggest that some rounds tend to have significantly longer selection times than other rounds.

```{r}
summary(model)

```
