---
title: "Day13"
author: "Olivia Wu"
date: "2024-04-15"
header-includes:
   - \usepackage{amsmath}
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tinytex)
library(readr)
library(ggplot2)
library(BSDA)
library(leaps)
library(olsrr)
library(car)
library(mosaic)
```
```{r, include=FALSE}
setwd("C:/Users/ozwu/OneDrive/Documents/SCHOOL/RS3")
HP <- read_csv("csv/CSV Data Set Files by Descriptive Title/HighPeaks.csv")
SAT <- read_csv("csv/CSV Data Set Files by Descriptive Title/SATGPA.csv")
setwd("Chapter 4")
```
\section*{Problem 4.20}

\quad a) We are 90\% confident that the true slope of the population regression lies in the interval (0.914, 1.240)
```{r,echo=FALSE}
model1 <- lm(Length ~ Time, data=HP)
summary(model1)
```

\quad b) The histogram is slightly skewed right. The slopes tend to be around 1.1.

```{r,echo=FALSE}
set.seed(123)
boot <- do(5000)*lm(Length ~ Time, data=resample(HP))
hist(boot$Time, xlab="Slopes",main="Histogram of Slopes for 5000 Bootstrap Samples")
```

\quad c) The mean is about 1.09, and the standard deviation is around 0.12. They are both just slightly above the numbers in our computer output of the original model.
```{r}
pt <- mean(boot$Time)
se <- sd(boot$Time)
c(pt,se)
```

\quad d) \textcolor{red}{pt estimate is the initial value}
```{r}
sum <- summary(model1)
paste("(",pt-qnorm(0.95)*se,",",pt+qnorm(0.95)*se,")")
paste("(",sum$coefficients[2,1]-qnorm(0.95)*se,",",sum$coefficients[2,1]+qnorm(0.95)*se,")")
```

\quad e) 
```{r}
lower <- quantile(boot$Time, 0.05)
upper <- quantile(boot$Time, 0.95)
paste("(",lower,",",upper,")")

```

\quad f)
```{r}
newlower <- 2*1.07711 - upper
newupper <- 2*1.07711 - lower
paste("(",newlower,",",newupper,")")
```

\quad g) The intervals are all very similar.

\section*{Problem 4.21}

Save initial model:
```{r}
model1 <- lm(Length ~ Time, data=HP)
```

Save initial standard deviation of the error term:
```{r}
initial <- summary(model1)$sigma
```

Simulate:
```{r,echo=FALSE}
set.seed(123)
boot <- do(5000)*lm(Length ~ Time, data=resample(HP))
hist(boot$sigma, xlab="Standard Deviation of Error", main="Histogram of Standard Deviation of Error")
```

Interval 1:
```{r}
pt <- mean(boot$sigma)
se <- sd(boot$sigma)
paste("(",initial+qnorm(0.05)*se,",",initial+qnorm(0.95)*se,")")
```

Interval 2:
```{r}
lower <- quantile(boot$sigma, 0.05)
upper <- quantile(boot$sigma,0.95)
paste("(",lower,",",upper,")")
```

Interval 3:
```{r}
paste("(",2*initial - upper,",",2*initial-lower,")")
```

\section*{Problem 4.23}

\quad a) The initial correlation is $r=$0.244. The histogram is roughly symmetric, and the normal probability plot is roughly linear, suggesting that the boostrap distribution is normal.

```{r}
initial <- cor(VerbalSAT~GPA, data=SAT)
boot <- do(5000)*cor(VerbalSAT~GPA, data=resample(SAT))
hist(boot$cor, xlab="Correlation", main="Histogram of Correlation")
qqnorm(boot$cor)
```

\quad b) The two intervals are (-0.107, 0.596) and (-0.090, 0.615). They are similar.

```{r,echo=FALSE}
#z interval with boostrap SE
se <- sd(boot$cor)
paste("(",initial+qnorm(0.025)*se,",",initial+qnorm(0.975)*se,")")
#quantile
lower <- quantile(boot$cor, 0.025)
upper <- quantile(boot$cor, 0.975)
paste("(",lower,",",upper,")")
```

\quad c) 0 is in both confidence intervals. We are not confident that there is a relationship between Verbal SAT scores and GPA.
