---
title: "Day12"
author: "Olivia Wu"
date: "2024-04-09"
header-includes:
   - \usepackage{amsmath}
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tinytex)
library(readr)
library(ggplot2)
library(BSDA)
library(leaps)
library(olsrr)
library(car)
library(mosaic)
```
```{r, include=FALSE}
setwd("C:/Users/ozwu/OneDrive/Documents/SCHOOL/RS3")
Cater <- read_csv("csv/CSV Data Set Files by Descriptive Title/Caterpillars.csv")
BB <- read_csv("csv/CSV Data Set Files by Descriptive Title/BaseballTimes2017.csv")
setwd("Chapter 4")
```

\section*{Problem 4.13}

If the mother is white, then the birth weight will be about $117.87 - 0 + 0 - 0 = 117.87$ oz.

If the mother is black, then the birth weight will be about $117.87 - 7.31 + 0 - 0 = 110.56$ oz.

If the mother is Hispanic, then the birth weight will be about $117.87 - 0 + 0.65 - 0 = 118.52$ oz.

If the mother is other, then the birth weight will be about $117.87 - 0 + 0 - 0.73 = 117.14$ oz.

\section*{Problem 4.14}

\quad a) Since the $p$-values of the $Hispanic$ and $Other$ predictors is greater than 0.05, we can not say that they are significant.

\quad b) $R^2 = 1.9\%$, so this model explains $1.9\%$ of the variability in the birth weight of a baby.

\quad c) $p<0.05$, so we can reject the null hypothesis and say that at least one of the predictors is important.

\section*{Probem 4.16}

\quad a) $R^2$ = 0.756, so about $76\%$ of the variability in log nitrogen asssimilation is explained by the model.
```{r,echo=FALSE}
model1 <- lm(LogNassim ~ LogMass, data=Cater)
summary(model1)
```

\quad b) $R^2 = 0.8348$, so about $83\%$ of the variability is explained in this model. This is more than the model from before.
```{r,echo=FALSE}
model2 <- lm(LogNassim ~ I(Instar==2) + I(Instar==3) + I(Instar==4) + I(Instar==5), data=Cater)
summary(model2)
```

\quad c) When the caterpillar is in stage 2, the log nitrogen assimilation is about -2.572. When it is in stage 3, then the log nitrogen assimilation is about -2.417.

\quad d) $R^2 = 0.8361$, so about $84\%$ of the variability is explained in this model. This is more than the model from before.
```{r,echo=FALSE}
model3 <- lm(LogNassim ~ LogMass+I(Instar==2) + I(Instar==3) + I(Instar==4) + I(Instar==5), data=Cater)
summary(model3)
```

\quad e) The $R^2$ is similar for both models, so I would check the $p$-value for the $logBodyMass$ predictor. $p=0.168 > 0.05$, so there is not enough evidence to show that $logBodyMass$ is a significant predictor.

\quad f) There are a lot of predictors to check, so we can use a nested $F$ test using the models found in (a) and (d). The $p$ value is less than 0.05, so the indicators of Instar are important.
```{r,echo=FALSE}
anova(model1, model3)
```

\section*{Problem 4.19}

\quad a) 

```{r,echo=FALSE}
model1 <- lm(Time ~ Pitchers + Attendance, data=BB)
summary(model1)
```

\quad b) Let's use $R^2$. $R^2 = 53.07$, so about $53.1\%$ of the variability is expalined by this model.

\quad c)
```{r,echo=FALSE}
set.seed(123)
many <- do(1)*cor(shuffle(Time)~Pitchers + Attendance, data=BB)
many = many$cor
head(many)
```

\quad d)
```{r,echo=FALSE}
set.seed(123)
many <- do(10000)*cor(shuffle(Time)~Pitchers + Attendance, data=BB)
many = (many$cor)^2
hist(many, breaks=seq(0, 1, 0.05), xlab="R^2", main="Histogram of Random Samples", col=c(0,0,0,0,0,0,0,0,0,0,"blue","blue"))
```

\quad e) Find the number of observations that have an $R^2$ greater than $0.5307$, and this divided by 10,000 is our $p$-value. This turns out to be $p = 0.0045 < 0.05$. There is enough evidence to suggest a relationship of predicting Time with Pitchers and Attendance.
```{r,echo=FALSE}
count <- 0
for(i in 1:10000){
  if(many[i] >= 0.5307)
    count <- count + 1
}
count/10000
```

\quad f) The summary output shows a $p-$value of 0.0156 for the $F$ statistic. This is greater than the $p$-value from our randomization test, but it is still less than $0.05$.