---
title: "Day2"
author: "Olivia Wu"
date: "2024-02-08"
header-includes:
   - \usepackage{amsmath}
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tinytex)
library(readr)
library(BSDA)
library(effectsize)
setwd("C:/Users/ozwu/OneDrive/Documents/SCHOOL/RS3")
WL7 <- read_csv("csv/CSV Data Set Files by Descriptive Title/WeightLossIncentive7.csv")
Run <- read_csv("csv/CSV Data Set Files by Descriptive Title/Marathon.csv")
D1S <- read_csv("csv/CSV Data Set Files by Descriptive Title/Day1Survey.csv")
Handwriting <- read_csv("csv/CSV Data Set Files by Descriptive Title/Handwriting.csv")
setwd("Chapter 0")
```

<!-- Complete Open-ended exercises from Chapter 0, pp.16-17: 23, 26, 27, 30, 31 -->

\textcolor{red}{Red shows the correct answer or where I should have added more detail}

\section*{Problem 0.23}
\textbf{Choose:} \quad There is a categorical explanatory variable (Control or Incentive) and the response variable is quantitative.
\newline Let $\mu_1$ represent the population mean weight loss at seven months for people without financial incentives and $\mu_2$ represent the population mean weight loss at seven months with financial incentives.
\newline Potential models for the two groups are:

\quad $Y=(\mu_1 + \epsilon)$ \textcolor{red}{$\sim N(0, \sigma_1)$}

\quad $Y=(\mu_2 + \epsilon)$ \textcolor{red}{$\sim N(0, \sigma_2)$}

\textbf{Fit:} \quad The means for the control and incentive groups are $4.639$ and $7.8$ pounds, respectively. Our models may be expressed as:

\quad$Y=(4.639 + \epsilon)$ \textcolor{red}{$\sim N(0, 7.8)$}

\quad$Y=(7.8 + \epsilon)$ \textcolor{red}{$\sim N(0, 12.06)$}

\textbf{Assess:} \quad We conduct a two-sample $\textit{t}$-test for the hypotheses:

\quad$H_0: \mu_1 - \mu_2 = 0$

\quad$H_a: \mu_1 - \mu_2 < 0$ \textcolor{red}{$\mu_1-\mu_2 \neq 0$}

\quad \textbf{Conditions} We assume independence and random assignment is given. The following normal probability plots are roughly linear, so we assume normality.
```{r, echo=FALSE, out.height="20%"}
qqnorm(WL7$Month7Loss[WL7$Group %in% "Control"]-mean(WL7$Month7Loss[WL7$Group %in% "Control"]), main="Normal Probability Plot for Control Group")
qqnorm(WL7$Month7Loss[WL7$Group %in% "Incentive"]-mean(WL7$Month7Loss[WL7$Group %in% "Incentive"]), main="Normal Probability Plot for Incentive Group")
```

```{r, echo=FALSE}
t.test(x=WL7$Month7Loss[WL7$Group %in% "Control"],
       y=WL7$Month7Loss[WL7$Group %in% "Incentive"],
       alternative = "less",
       mu = 0)
```
Since $p=0.2113 > 0.05$ \textcolor{red}{$p=0.4226>0.05$}, we fail to reject the null hypothesis.

\textbf{Use:} \quad There is not enough evidence to suggest that the beneficial effects of financial incentives still apply to the weight losses at the seven-month point. 

\section*{Problem 0.26}
```{r, include=FALSE}
short <- Run$PaceMin[Run$Short %in% 1]
short <- short[!is.na(short)]
long <- Run$PaceMin[Run$Short %in% 0]
long <- long[!is.na(long)]
```
\textbf{Choose:} \quad There is a categorical explanatory variable (Short or Long) and the response variable (Pace) is quantitative.
\newline Let $\mu_1$ represent the population mean pace for short runs and $\mu_2$ represent the population mean pace for long runs.
\newline Potential models for the two groups are:

\quad $Y=\mu_1 + \epsilon$

\quad $Y=\mu_2 + \epsilon$

\textbf{Fit:} \quad The means for the short and long groups are $7.96$ and $8.16$ minutes per mile, respectively. Our models may be expressed as:

\quad$Y=7.96 + \epsilon$

\quad$Y=8.16 + \epsilon$

\textbf{Assess:} \quad We conduct a two-sample $\textit{t}$-test for the hypotheses:

\quad$H_0: \mu_1 - \mu_2 = 0$

\quad$H_a: \mu_1 - \mu_2 < 0$

\quad \textbf{Conditions} We assume randomness and independence. \textcolor{red}{There are more than 30 observations for both groups, so the normality conditions is satisfied.} This is further supported by the roughly linear normal probability plots shown below.
```{r, echo=FALSE, out.height="20%"}
qqnorm(short-mean(short), main="Normal Probability Plot for Short Runs")
qqnorm(long-mean(long), main="Normal Probability Plot for Long Runs")
```

```{r, echo=FALSE}
t.test(x=short,
       y=long,
       alternative = "less",
       mu = 0)
```
$p=0 < 0.05$ so we reject the null hypothesis. There is a statistically significant difference in pacing for short and long runs.

\textbf{Use: } \quad There is enough evidence to suggest that the runner tends to run faster on short runs than on long runs.

\section*{Problem 0.27}
```{r, include=FALSE}
young_pace <- Run$PaceMin[Run$After2004 %in% 0]
young_pace <- young_pace[!is.na(young_pace)]
old_pace <- Run$PaceMin[Run$After2004 %in% 1]
old_pace <- old_pace[!is.na(old_pace)]

young_dist <- Run$Miles[Run$After2004 %in% 0]
young_dist <- young_dist[!is.na(young_dist)]
old_dist <- Run$Miles[Run$After2004 %in% 1]
old_dist <- old_dist[!is.na(old_dist)]
```
\begin{enumerate}
\item[a)] \textbf{Choose: } \quad $Y = \mu_i + \epsilon$ where $\mu_1$ represents the average running pace from 2002-2004, and $\mu_2$ represents the average running pace from 2005-2006.

\textbf{Fit:} \quad $Y = 7.914 + \epsilon$ for 2002-2004 \\ \quad \quad $Y = 8.411 + \epsilon$ for 2005-2006

\textbf{Assess:} \quad We test for the hypotheses:

\quad \quad $H_0: \mu1 - \mu2 = 0$

\quad \quad $H_a: \mu1 - \mu2 \neq 0$

\quad \quad The conditions have been verified in Problem 0.26
\end{enumerate}
```{r, echo=FALSE}
t.test(x=young_pace,
       y=old_pace,
       alternative="two.sided",
       mu=0)
```
\quad \quad $p\approx 0 < 0.05$ so we reject the null hypothesis. There is a statistically significant difference in pacing for runs before and after 2004.

\quad \textbf{Use: } \quad There is enough evidence to suggest that the runner had different pacings when he was young compared to when he was old.
\begin{enumerate}
\item[b)] \textbf{Choose: } \quad $Y = \mu_i + \epsilon$ where $\mu_1$ represents the average daily distance from 2002-2004, and $\mu_2$ represents the average daily distance from 2005-2006.

\textbf{Fit:} \quad $Y = 7.492 + \epsilon$ for 2002-2004 \\ \quad \quad $Y = 6.629 + \epsilon$ for 2005-2006

\textbf{Assess:} \quad We test for the hypotheses:

\quad \quad $H_0: \mu1 - \mu2 = 0$

\quad \quad $H_a: \mu1 - \mu2 \neq 0$

\quad \quad The conditions have been verified in Problem 0.26
\end{enumerate}
```{r, echo=FALSE}
t.test(x=young_dist,
       y=old_dist,
       alternative="two.sided",
       mu=0)
```
\quad \quad $p\approx 0 < 0.05$ so we reject the null hypothesis. There is a statistically significant difference in distance ran per day before and after 2004.

\quad \textbf{Use: } \quad There is enough evidence to suggest that the runner ran different distances per day when he was young compared to when he was old.

\section*{Problem 0.30}
```{r, include=FALSE}
men_pulse <- D1S$Pulse[D1S$Sex=="M"]
wom_pulse <- D1S$Pulse[D1S$Sex=="F"]
men_pulse <- men_pulse[!is.na(men_pulse)]
wom_pulse <- wom_pulse[!is.na(wom_pulse)]
```
\begin{enumerate}
\item[a)] effect size = $\frac{66.65 - 67.82}{11.31} = 0.103$, so there is a small difference in pulses between men and women
\item[b)] effect size = $\frac{|7.96 - 8.16|}{0.48} = 0.407$, so there is a moderate effect of changing the distance of runs on the pace.

\end{enumerate}
\section*{Problem 0.31}
```{r, include=FALSE}
men <- Handwriting$Both[Handwriting$Gender %in% 0]
wom <- Handwriting$Both[Handwriting$Gender %in% 1]
men <- men[!is.na(men)]
wom <- wom[!is.na(wom)]
```
\begin{enumerate}
\item[a)] effect size = 0.228, so there is a small effect of training before or after 2004 had on the mean miles per day for training.
\item[b)] effect size = 1.072, so there is a large difference in the guessing abilities between men and women.
\end{enumerate}